\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{url}
\usepackage[hidelinks]{hyperref}


\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}


\begin{document}

\title{Quadruped walking algorithms\\ Spline Approach for Trajectory Generation}

\author{\IEEEauthorblockN{Team Member: Jan Górski}
\IEEEauthorblockA{jagor24@student.sdu.dk}
\and
\IEEEauthorblockN{Author: Alan Bejnarowicz}
\IEEEauthorblockA{albej24@student.sdu.dk}
}
\maketitle

\begin{center}
    Project repository: \href{https://github.com/AlanBejnarowicz/AECS}{https://github.com/AlanBejnarowicz/AECS}
\end{center}



\begin{IEEEkeywords}
\end{IEEEkeywords}
\textit{Qdruped robots, walking algorithms, spline interpolation, 
trajectory generation, smooth motion planning}

\section{Introduction}
\input{sections/introduction.tex}

\section{Description of the problem}
\input{sections/problem.tex}

\section{Problems to be solved}
\input{sections/to_be_solve.tex}

\section{Inverse Kinematics}
\input{sections/IK.tex}


\section{Phase and Spline Trajectory Generation}
\input{sections/spline.tex}


\section{PID balancing controller}
\input{sections/balancing.tex}

\section{Control system}
\input{sections/system.tex}

\section{Results}
\input{sections/results.tex}


\section {All YouTube videos links}
YouTube videos demonstrating the results can be found here:
\begin{itemize}
    \item Fast walking: \href{https://youtu.be/nRwTH8aU0jQ}{https://youtu.be/nRwTH8aU0jQ}
    \item Heavy terrain: \href{https://youtu.be/4OVWzleJ\_GU}{https://youtu.be/4OVWzleJ\_GU}
    \item No PID funny setup walking: \href{https://www.youtube.com/watch?v=eI8ZH1-Hwkk}{https://www.youtube.com/watch?v=eI8ZH1-Hwkk}
    \item Flat terrain no PID balancing: \href{https://youtu.be/eI8ZH1-Hwkk}{https://youtu.be/eI8ZH1-Hwkk}
\end{itemize}


\begin{thebibliography}{00}
\bibitem{unitree-mujoco-github}
Unitree Robotics, "unitree\_mujoco" GitHub repository.
Available: \url{https://github.com/unitreerobotics/unitree_mujoco}. 
Accessed: Dec. 1, 2025.

\bibitem{unitree-go2}
Unitree Robotics, "Unitree GO2 Robot" Product Page.
Available: \url{https://shop.unitree.com/products/unitree-go2?srsltid=AfmBOooo_NzRU6B7Nf0OCNzLnS0lI8Q6H5uuD0nauSsT0dyTkfN_iFYb}. 
Accessed: Dec. 1, 2025.

\bibitem{go2_inverse_kinematics}
Unitree Go2 Inverse Kinematics Article.
Available: \url{https://observablehq.com/@christophe-yamahata/inverse-kinematics-go2-robot}. 
Accessed: Dec. 1, 2025.


\bibitem{disney-imaginiering-bipedal-robots} Disney Imagineering Bipedal Robots. Available:
\url{https://www.youtube.com/watch?v=-cfIm06tcfA}.
Accessed: Dec. 1, 2025.

\bibitem{mujoco}E. Todorov, T. Erez and Y. Tassa, "MuJoCo: A physics engine for model-based control," 2012 IEEE/RSJ International Conference on Intelligent Robots and Systems, Vilamoura-Algarve, Portugal, 2012, pp. 5026-5033, doi: 10.1109/IROS.2012.6386109.
keywords: {Engines;Optimization;Computational modeling;Heuristic algorithms;Dynamics;Mathematical model},

\bibitem{unitree-mujoco-github} Unitree Robotics, "unitree\_mujoco" GitHub repository.
\url{https://github.com/unitreerobotics/unitree_mujoco}
Accessed: Dec. 1, 2025.\

\bibitem{disney-control-bipedal} Design and Control of a Bipedal Robotic Character 
\url{https://la.disneyresearch.com/publication/design-and-control-of-a-bipedal-robotic-character/}
Accessed: Dec. 1, 2025.

\bibitem{deep-tracking-control} DTC: Deep Tracking Control, ETH Zürich
\url{https://www.science.org/doi/10.1126/scirobotics.adh5401}

\bibitem{deep-tracking-control-video} Video of DTC: Deep Tracking Control, ETH Zürich
\url{https://www.youtube.com/watch?v=nipH-yl8lR0}


\bibitem{pedro2024quadruped}
G.~D.~G. Pedro, G.~Bermudez, V.~S. Medeiros, H.~J.~d.~C. Neto, L.~G.~D.~d. Barros, G.~Pessin, M.~Becker, G.~M. Freitas, and T.~Boaventura, "Quadruped Robot Control: An Approach Using Body Planar Motion Control, Legs Impedance Control and B\'ezier Curves," Sensors, vol. 24, art. no. 3825, 2024. doi: 10.3390/s24123825. [Online]. Available: \url{https://doi.org/10.3390/s24123825}

\end{thebibliography}




\end{document}
